Nitric oxide feedback to ciliary photoreceptor cells gates a UV avoidance circuit

### 2023-06-14 Manuscript/Manuscript.Rmd

Here we uncovered an essential function for NO signalling in larval UV/violet-light avoidance behaviour.
In *Platynereis* larvae, UV/violet avoidance is mediated by brain ciliary photoreceptor cells (cPRCs) and is characterised by downward swimming [@Veraszto2018].
The cPRCs express a ciliary-type opsin, c-opsin1 [@Arendt2004] that forms a UV-absorbing bistable photopigment with an absorption maximum around 384 nm [@tsukamoto2017; @Veraszto2018; @Veedin2021].
Upon UV/violet exposure, the cPRC show a characteristic biphasic calcium response that is *c-opsin1* dependent.
UV/violet avoidance is also *c-opsin1*-dependent and is defective in *c-opsin1* mutants [@Veraszto2018].
Here we show that *Platynereis* *NOS* is expressed in interneurons of the cPRC circuit and is required for UV/violet-avoidance.
By combining calcium imaging across the fully-mapped cPRC circuit [@Veraszto2018] with genetic perturbations and mathematical modelling, we describe how NO tunes circuit dynamics through non-synaptic retrograde signalling to cPRCs.
This delayed neuroendocrine feedback integrates UV/violet exposure to induce a short-term memory manifested in altered circuit activity and an aversive behavioural response.

@@

We identified a single *nitric oxide synthase* (*NOS*) gene in the *Platynereis dumerilii* genome and transcriptome data.
Phylogenetic analysis of NOS proteins indicate that *Platynereis* NOS belongs to an orthology group of bilaterian NOS sequences (Figure 1---figure supplement 1).
To characterise the expression pattern of *NOS* we used in situ hybridization chain reaction (HCR) and transient transgenesis.
In two- and three-day-old larvae, we detected *NOS* expression in four cells (two of them weakly expressing) in the apical organ region (Figure 1D and Figure 1---figure supplement 2).
*NOS* was also expressed in the region of the visual eyes (adult eyes) and the pigmented eyespots (Figure 1---figure supplement 2).
The four apical organ cells, but not the eyes, were also labelled with a *NOS* reporter construct driving palmitoylated-tdTomato (Figure 1E).
This reporter also revealed the axonal projections of these central NOS-expressing neurons.
The position and morphology of the four *NOS+* cells allowed us to identify the same four cells as four interneurons (INNOS) in our three-day-old whole-body *Platynereis* volume EM data [@williams2017; @veraszto2020] (Figure 1B,C).
In the synaptic connectome, the INNOS cells are postsynaptic to the UV-sensory cPRCs and presynaptic to the INRGWa interneurons, which are also cPRC targets (Figure 1C,F).
The projections of INNOS cells are segregated into input (dendritic) and output (axonal) compartments, with cPRC inputs occurring on the dendritic part in the dense neurosecretory plexus.
INNOS output synapses form in the more ventral projection region (Figure 1---figure supplement 3).
INRGWa neurons synapse on the head serotonergic ciliomotor neurons (Ser-h1), which synapse on the prototroch ciliary band and the cholinergic MC ciliomotor neurons (Figure 1C,F) [@veraszto2017].

@@

We next tested whether NO signalling regulates UV/violet avoidance.
To achieve this, we generated two *Platynereis* *NOS* knockout lines with the CRISPR/Cas9 method.
We recovered two deletions (NOSΔ11/Δ11 and Δ23/Δ23), both frame-shift mutations leading to an early stop codon and thus likely representing null alleles (Figure 3---figure supplement 1A).
We could establish a homozygous line for both mutations indicating that NOS is not an essential gene in *Platynereis*.
To quantify UV avoidance, we recorded the trajectories of freely swimming wild type and mutant larvae in vertical columns, illuminated laterally from two opposite sides with 395 nm UV light (Figure 3A and Figure 3---figure supplement 1B).
As previously shown, wild-type larvae swim downward following non-directional UV/violet light stimulation [@Veraszto2018].
In contrast, both two- and three-day-old homozygous *NOS*-mutant larvae showed a strongly diminished UV-avoidance response (Figure 3A, B and Figure 3---figure supplement 1B,C).
This phenotype is similar to the defective UV-avoidance of *c-opsin1* mutant larvae [@Veraszto2018] and reveals a requirement for NOS in UV-avoidance behaviour.
Wild type but not mutant larvae also showed an increase in swimming speed under UV light that may be due to downward swimming trajectories (swimming in the direction of gravity) (Figure 3B and Figure 3---figure supplement 1C).
We also tested directional phototaxis, by exposing larvae to 480 nm directional collimated light from the top of the column.
Three-day-old but not two-day-old *NOS*-mutant larvae also showed reduced phototactic behaviour, suggesting a function for *NOS* in the visual eyes that mediate three-day-old phototaxis [@Randel2014a] (Figure 3D and Figure 3---figure supplement 1G).

To distinguish between an acute and developmental function of NOS in light responses, we next tested larvae exposed to the NOS inhibitor L-NAME.
Larvae incubated for 5 min in 0.1 mM or 1 mM L-NAME showed a dose-dependent inhibition of UV avoidance.
In contrast, phototaxis was not affected (Figure 3C, E).
Overall, our results indicate an acute requirement for NOS signalling in UV-avoidance and a possible indirect, developmental role in the visual system, reminiscent of the function of NO signalling in *Drosophila* eye development [@Gibbs1998a].

@@

To investigate how NO signalling alters the dynamics of the cPRC circuit, we carried out calcium imaging experiments.
We ubiquitously expressed the calcium sensor GCaMP6s in larvae and imaged calcium signals during 405 nm stimulation of the cPRCs.
As we have shown previously, a 20-sec local stimulation of cPRC cilia led to a transient increase in cPRC calcium levels, followed by a transient decrease [@Veraszto2018].
After \~20-sec, calcium levels in cPRCs were raising again, reaching higher levels than at the start of the stimulus -- a response that may involve depolarisation (Figure 4A, B).
This activation phase occurs after the 20 sec stimulation period and is likely due to a delayed neuroendocrine feedback [@Veraszto2018].
To determine whether NO mediates such a feedback, we repeated the experiment in *NOS*-mutant larvae.
While we detected the initial activation phase followed by inhibition, in homozygous *NOS*-mutants for both CRISPR alleles this was not followed by delayed activation.
Instead, calcium levels dropped to a low steady-state level (Figure 4A, B).
We thus identified a requirement for NO signalling in the late-phase activation of cPRCs.

@@

We aimed next to identify the NO receptor in the cPRCs.
NO generally acts via soluble guanylate cyclases (sGC), belonging to the guanylate cyclase family with a CYC domain (PFAM domain: PF00211).
NO binding to the heme group of sGC leads to increased cyclic guanosine monophosphate (cGMP) production.
Analysis of sGCs in *Platynereis* indicated that these genes are not expressed in any of the cells of the cPRC circuit [@veraszto2017].
Recently, Moroz and coworkers reported an atypical but widely conserved family of guanylyl cyclases with a NIT (nitrite/nitrate sensing) domain (PF08376) (NIT-GC) as potential mediators of NO signalling [@Moroz2020].
To identify NIT-GCs in *Platynereis*, we searched transcriptome resources and retrieved 15 potential NIT-GC homologs (Figure 4---figure supplement 1 and 2).
To analyse the relationship of these sequences to metazoan NIT-GCs, we retrieved protein sequences with a CYC domain from the transcriptome and genome databases of 45 metazoan and 2 choanoflagellate species.
We carried out cluster analysis and did phylogenetic reconstruction on a group of membrane-bound guanylyl cyclases with sGCs as an outgroup.
In agreement with Moroz et al. [@Moroz2020], we found a group of GCs with NIT domains with representatives in placozoans, cnidarians, some ecdysozoans, echinoderms, and lophotrochozoans.
The 15 *Platynereis* sequences belonged to several deeply diverged clades in the phylogenetic tree (Figure 4---figure supplement 1 and 2).

@@

To investigate how NO and NIT-GC signalling influence the dynamics of the cPRC circuit, we imaged calcium signals from postsynaptic neurons in wild type, mutant and morphant larvae.
We were able to image the activity of all neurons in the cPRC circuit (INNOS, INRGWa, Ser-h1 and MC).
The MC cell was identified based on its position and intrinsic activity [@veraszto2017].
To unambiguously identify all other cells from which we recorded calcium signals, we developed an on-slide immunostaining method (Figure 5---figure supplement 1A).
We used the cell-specific antibody markers against RYamide (INNOS) (Figure 5---figure supplement 1B-D), RGWamide (INRGWa) and serotonin (Ser-h1) [@Conzelmann2011] to immunostain agar-embedded larvae following calcium imaging.
Based on the position of the nuclei, we could correlate live and fixed samples at a single-cell precision (Figure 5A,B).
Due to the stereotypy of the larvae, we could also identify neurons based on their position and calcium activity in activity-correlation maps (Figure 5C).

@@

Next, we imaged calcium signals from Ser-h1 and MC neurons in wild type and *NOS* mutant larvae.
Ser-h1 cells showed an activation profile that correlated with cPRC activity, including a reduction in calcium during stimulation followed by rebound, a response that was defective in *NOS* mutants (Figure 5I).
MC cells showed sustained activation, including a late-phase that was lacking in *NOS* mutants (Figure 5I).
These data suggest that during 405 nm stimulation the Ser-h1 cells are inhibited and MC cells are activated, and this regulation is NO-dependent.
This pattern is expected to inhibit ciliary activity in the prototroch but not in the other ciliary bands, triggering NO-dependent downward swimming.

@@

In the INNOS cells, we assume that excitatory synaptic input from cPRC (or rebound from tonic inhibition) leads to a rise in Ca^2+^ leading to NO production via NOS.
This input is NIT-GC2-dependent.
In the INRGWa cells, we model a decrease in Ca^2+^ based on an inhibitory UV-dependent synaptic signal from the cPRCs.
We further assume the existence of direct excitatory coupling between cPRC Ca^2+^ levels and INRGWa Ca^2+^ to account for the late effects of cPRC on INRGWa (Figure 6A).
The UV-dependent and Ca^2+^-dependent signals may be mediated by different transmitters released by cPRCs during distinct phases of their activation cycle.
In addition, we assume a direct inhibitory coupling between INNOS Ca^2+^ and INRGWa Ca^2+^.
Finally, in all variables, we assumed a linear decay and constant production to set a steady state (Figure 6A).
Since the aim of the model is to capture the normalised fluorescence data, the model is nondimensionalised.
UV stimulation is modelled as a square pulse.
To find model parameters producing an output fitting the experimental data we employed a global optimisation method known as a genetic algorithm (GA).

Through this optimisation procedure, we found parameters that gave a very good fit to our experimental data under all conditions.
We could fit to mean Ca^2+^ values but also individual calcium transients (Figure 6B, Figure 6--figure supplement 1).
Our model only includes a minimal set of parameters and assumptions of interactions that are required to describe the dynamics of cPRC, INNOS and INRGWa in wild type and loss-of-function conditions (Figure 6A, B).
The model highlights that cPRC phototransduction employs distinct pathways that operate on different time scales and differentially influence cPRC Ca^2+^ levels.
The coupling between cPRCs and interneurons also requires different signalling mechanisms, either through distinct neurotransmitters or receptors expressed in the different cells.

@@

@@

```{r echo=FALSE,fig.cap="**Figure 6. Mathematical modelling of cPRC circuit dynamics during UV stimulation and potential signalling mechanisms.**  **(A)** Diagram for **(B)** **(C)** Dot plot of genes (columns) expressed in three types of cells (rows) in the cPRC circuit using single cell RNA-Seq. The size of the dots is expressed in proportion to the percentage of cells expressing that gene relative to all cells. The colours represent the normal logarithm of the number of transcripts in the cells expressing the gene. **(D)** Schematic diagram of the signalling pathway of the cPRC circuit, focusing on the NO feedback."}

knitr::include_graphics(path = "figures/Fig6.png")

@@

Compartmentalised signalling also occurs in peptidergic modulatory systems and can enable selective network activity during specific behaviours.
In the UV-avoidance circuit of *Drosophila* larvae, a peptidergic hub neuron Dp7 links UV-sensory neurons (v'td2) and motor circuits.
Dp7 expresses an an insulin-like peptide Ilp7 that is required for acute and sustained UV avoidance.
Ilp7 signalling occurs at a functionally and morphologically distinct dendritic compartment of Dp7, segregated from other sensory-motor pathways involving Dp7 [@Imambocus2022].

@@

In the *Platynereis* circuit, our mathematical model indicates that the onset, magnitude and duration of the NO-dependent signal depends on the intensity and duration of the UV/violet stimulus.
This suggests that the NO-dependent memory trace also encodes the magnitude and duration of the stimulus.

@@

```{r echo=FALSE}
library(readxl)
key_resource_table <- read_excel("key_resource_table/key_resource_tale.xls")
df_key_resource_table <- as.data.frame(key_resource_table)
knitr::kable(df_key_resource_table, format = "html", booktabs = TRUE)
```

@@

This work was funded by the Wellcome Trust (214337/Z/18/Z).
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 101020792).
KJ has been supported by a JSPS Postdoctoral fellowhip, LAYG by a BBSRC Discovery fellowship (BB/W010305/1), PS by a Wellcome Trust Institutional Strategic Support Award (204909/Z/16/Z).

>>>>

Here we uncovered an essential function for NO signalling in larval UV/violet-light avoidance behaviour.
In *Platynereis* larvae, UV/violet avoidance is mediated by brain ciliary photoreceptor cells (cPRCs) and is characterised by downward swimming [@Veraszto2018].
The cPRCs express a ciliary-type opsin, c-opsin1 [@Arendt2004] that forms a UV-absorbing bistable photopigment with an absorption maximum around 384 nm [@tsukamoto2017; @Veraszto2018; @Veedin2021].
Upon UV/violet exposure, the cPRCs show a characteristic biphasic calcium response that is *c-opsin1* dependent.
UV/violet avoidance is also *c-opsin1*-dependent and is defective in *c-opsin1* mutants [@Veraszto2018].
Here we show that *Platynereis* *NOS* is expressed in interneurons of the cPRC circuit and is required for UV/violet-avoidance.
By combining calcium imaging across the fully-mapped cPRC circuit [@Veraszto2018] with genetic perturbations and mathematical modelling, we describe how NO tunes circuit dynamics through non-synaptic retrograde signalling to cPRCs.
This delayed neuroendocrine feedback integrates UV/violet exposure to induce a short-term memory manifested in altered circuit activity and an aversive behavioural response.

@@

We identified a single *nitric oxide synthase* (*NOS*) gene in the *Platynereis dumerilii* genome and transcriptome data.
Phylogenetic analysis of NOS proteins indicate that *Platynereis* NOS belongs to an orthology group of bilaterian NOS sequences (Figure 1---figure supplement 1).
To characterise the expression pattern of *NOS* we used in situ hybridization chain reaction (HCR) and transient transgenesis.
In two- and three-day-old larvae, we detected *NOS* expression in four cells (two of them weakly expressing) in the apical organ region (Figure 1D and Figure 1---figure supplement 2).
*NOS* was also expressed in the region of the visual eyes (adult eyes) and the pigmented eyespots (Figure 1---figure supplement 2).
The four apical organ cells, but not the eyes, were also labelled with a *NOS* reporter construct driving palmitoylated-tdTomato (Figure 1E).
This reporter also revealed the axonal projections of these central NOS-expressing neurons.
The position and morphology of the four *NOS+* cells allowed us to identify the same four cells as four interneurons (INNOS) in our three-day-old whole-body *Platynereis* volume EM data [@williams2017; @veraszto2020] (Figure 1B, C).
In the synaptic connectome, the INNOS cells are postsynaptic to the UV-sensory cPRCs and presynaptic to the INRGWa interneurons, which are also cPRC targets (Figure 1C,F).
The projections of INNOS cells are segregated into input (dendritic) and output (axonal) compartments, with cPRC inputs occurring on the dendritic part in the dense neurosecretory plexus.
INNOS output synapses form in the more ventral projection region (Figure 1---figure supplement 3).
INRGWa neurons synapse on the head serotonergic ciliomotor neurons (Ser-h1), which synapse on the cholinergic MC ciliomotor neuron and cells of the prototroch ciliary band (Figure 1C,F) [@veraszto2017].

@@

We next tested whether NO signalling regulates UV/violet avoidance.
To achieve this, we generated two *Platynereis* *NOS* knockout lines with the CRISPR/Cas9 method.
We recovered two deletions (NOSΔ11/Δ11 and Δ23/Δ23), both frame-shift mutations leading to an early stop codon and thus likely representing null alleles (Figure 3---figure supplement 1A).
We could establish a homozygous line for both mutations indicating that NOS is not an essential gene in *Platynereis*.
To quantify UV avoidance, we recorded the trajectories of freely swimming wild type and mutant larvae in vertical columns, illuminated laterally from two opposite sides with 395 nm UV light (Figure 3A and Figure 3---figure supplement 1B).
As previously shown, wild-type larvae swim downward following non-directional UV/violet light stimulation [@Veraszto2018].
In contrast, both two- and three-day-old homozygous *NOS*-mutant larvae showed a strongly diminished UV-avoidance response (Figure 3A, B and Figure 3---figure supplement 1B, C).
This phenotype is similar to the defective UV-avoidance of *c-opsin1* mutant larvae [@Veraszto2018] and reveals a requirement for NOS in UV-avoidance behaviour.
Wild type but not mutant larvae also showed an increase in swimming speed under UV light that may be due to downward swimming trajectories (swimming in the direction of gravity) (Figure 3B and Figure 3---figure supplement 1C).
We also tested directional phototaxis, by exposing larvae to 480 nm directional collimated light from the top of the column.
Three-day-old but not two-day-old *NOS*-mutant larvae also showed reduced phototactic behaviour, suggesting a function for *NOS* in the visual eyes that mediate three-day-old phototaxis [@Randel2014a] (Figure 3D and Figure 3---figure supplement 1G).

To distinguish between an acute and developmental function of NOS in light responses, we also tested larvae exposed to the NOS inhibitor L-NAME.
Larvae incubated for 5 min in 0.1 mM or 1 mM L-NAME showed a dose-dependent inhibition of UV avoidance.
In contrast, phototaxis was not affected (Figure 3C, E).
Overall, our results indicate an acute requirement for NOS signalling in UV-avoidance and a possible indirect, developmental role in the visual system, reminiscent of the function of NO signalling in *Drosophila* eye development [@Gibbs1998a].

@@

To investigate how NO signalling alters the dynamics of the cPRC circuit, we carried out calcium imaging experiments.
We ubiquitously expressed the calcium sensor GCaMP6s in larvae and imaged calcium signals during 405 nm stimulation of the cPRCs.
As we have shown previously, a 20-sec local stimulation of cPRC cilia led to a transient increase in cPRC calcium levels, followed by a transient decrease [@Veraszto2018].
After \~20 sec, calcium levels in cPRCs were raising again, reaching higher levels than at the start of the stimulus -- a response that may involve depolarisation (Figure 4A, B).
This activation phase occurs after the 20 sec stimulation period and is likely due to a delayed neuroendocrine feedback [@Veraszto2018].
To determine whether NO mediates such a feedback, we repeated the experiment in *NOS*-mutant larvae.
While we detected the initial activation phase followed by inhibition, in homozygous *NOS*-mutants for both CRISPR alleles this was not followed by delayed activation.
Instead, calcium levels dropped to a low steady-state level (Figure 4A, B).
We thus identified a requirement for NO signalling in the late-phase activation of cPRCs.

@@

We aimed next to identify the NO receptor in the cPRCs.
NO generally acts via soluble guanylate cyclases (sGC), belonging to the guanylate cyclase family with a CYC domain (PFAM domain: PF00211).
NO binding to the heme group of sGC leads to increased cyclic guanosine monophosphate (cGMP) production.
Analysis of sGCs in *Platynereis* indicated that these genes are not expressed in the cPRCs [@veraszto2017] (not shown).
Recently, Moroz and coworkers reported an atypical but widely conserved family of guanylyl cyclases with a NIT (nitrite/nitrate sensing) domain (PF08376) (NIT-GC) as potential mediators of NO signalling [@Moroz2020].
To identify NIT-GCs in *Platynereis*, we searched transcriptome resources and retrieved 15 potential NIT-GC homologs (Figure 4---figure supplement 1 and 2).
To analyse the relationship of these sequences to metazoan NIT-GCs, we retrieved protein sequences with a CYC domain from the transcriptome and genome databases of 45 metazoan and 2 choanoflagellate species.
We carried out cluster analysis and did phylogenetic reconstruction on a group of membrane-bound guanylyl cyclases with sGCs as an outgroup.
In agreement with Moroz et al. [@Moroz2020], we found a group of GCs with NIT domains with representatives in placozoans, cnidarians, some ecdysozoans, echinoderms, and lophotrochozoans.
The 15 *Platynereis* sequences belonged to several deeply diverged clades in the phylogenetic tree (Figure 4---figure supplement 1 and 2).

@@

To investigate how NO and NIT-GC signalling influence the dynamics of the cPRC circuit, we imaged calcium signals from postsynaptic neurons in wild type, mutant and morphant larvae.
We were able to image the activity of all neurons in the cPRC circuit (INNOS, INRGWa, Ser-h1 and MC).
The MC cell was identified based on its position and intrinsic activity [@veraszto2017].
To unambiguously identify all other cells from which we recorded calcium signals, we developed an on-slide immunostaining method (Figure 5---figure supplement 1A).
We used the cell-specific antibody markers against RYamide (INNOS) (Figure 5---figure supplement 1B-D), RGWamide (INRGWa) and serotonin (Ser-h1) [@Conzelmann2011] to immunostain agar-embedded larvae following calcium imaging.
Based on the position of the nuclei, we could correlate live and fixed samples at a single-cell precision (Figure 5A, B).
Due to the stereotypy of the larvae, we could also identify neurons based on their position and calcium activity in activity-correlation maps (Figure 5C).

@@

Next, we imaged calcium signals from Ser-h1 and MC neurons in wild type and *NOS* mutant larvae.
Ser-h1 cells showed an activation profile that correlated with cPRC activity, including a reduction in calcium during stimulation followed by rebound, a response that was defective in *NOS* mutants (Figure 5I).
MC cells showed sustained activation, including a late-phase that was lacking in *NOS* mutants (Figure 5I).
These data suggest that during 405 nm stimulation the Ser-h1 cells are inhibited and MC cells are activated, and this regulation is NO-dependent.
This pattern is expected to inhibit ciliary activity in the prototroch but not in the other ciliary bands (with no Ser-h1 or MC synapses), triggering NO-dependent downward swimming.

@@

In the INNOS cells, we assume that excitatory synaptic input from cPRC (or rebound from tonic inhibition) leads to a rise in Ca^2+^ leading to NO production via NOS.
This input is NIT-GC2-dependent.
In the INRGWa cells, we model a decrease in Ca^2+^ based on an inhibitory UV-dependent synaptic signal from the cPRCs.
We further assume the existence of direct excitatory coupling between cPRC Ca^2+^ levels and INRGWa Ca^2+^ to account for the late effects of cPRC on INRGWa (Figure 6A).
The UV-dependent and Ca^2+^-dependent signals may be mediated by different transmitters released by cPRCs during distinct phases of their activation cycle.
In addition, we assume a direct inhibitory coupling between INNOS Ca^2+^ and INRGWa Ca^2+^.
Finally, in all variables, we assumed a linear decay and constant production to set a steady state (Figure 6A).
Since the aim of the model is to capture the normalised fluorescence data, the model is nondimensionalised.
UV stimulation is modelled as a square pulse.

To find model parameters producing an output fitting the experimental data we employed a global optimisation method known as a genetic algorithm (GA).
Through this optimisation procedure, we found parameters that gave a very good fit to our experimental data under all conditions.
We could fit to mean Ca^2+^ values but also individual calcium transients (Figure 6B, Figure 6--figure supplement 1).
Our model only includes a minimal set of parameters and assumptions of interactions that are required to describe the dynamics of cPRC, INNOS and INRGWa in wild type and loss-of-function conditions (Figure 6A, B).
The model highlights that cPRC phototransduction employs distinct pathways that operate on different time scales and differentially influence cPRC Ca^2+^ levels.
The coupling between cPRCs and interneurons also requires different signalling mechanisms, either through distinct neurotransmitters or receptors expressed in the different cells.

@@

```{r echo=FALSE,fig.cap="**Figure 6. Mathematical modelling of cPRC circuit dynamics during UV stimulation and potential signalling mechanisms.**  **(A)** Diagram for **(B)** **(C)** Dot plot of genes (columns) expressed in three types of cells (rows) in the cPRC circuit using single cell RNA-Seq. The size of the dots is expressed in proportion to the percentage of cells expressing that gene relative to all cells. The colours represent the normal logarithm of the number of transcripts in the cells expressing the gene. **(D)** Schematic diagram of the signalling pathway of the cPRC circuit, focusing on the NO feedback."}
knitr::include_graphics(path = "figures/Fig6.png")
```

@@

@@

Compartmentalised signalling also occurs in peptidergic modulatory systems and can enable selective network activity during specific behaviours.
In the UV-avoidance circuit of *Drosophila* larvae, a peptidergic hub neuron Dp7 links UV-sensory neurons (v'td2) and motor circuits.
Dp7 expresses an insulin-like peptide Ilp7 that is required for acute and sustained UV avoidance.
Ilp7 signalling occurs at a functionally and morphologically distinct dendritic compartment of Dp7, segregated from other sensory-motor pathways involving Dp7 [@Imambocus2022].

@@

In the *Platynereis* circuit, our mathematical model indicates that the magnitude of the NO-dependent signal depends on the intensity and duration of the UV/violet stimulus.
This suggests that the NO-dependent memory trace also encodes the intensity and duration of the stimulus.

@@

```{r echo=FALSE}
library(readxl)
key_resource_table <- read_excel("key_resource_table/key_resource_table.xls")
df_key_resource_table <- as.data.frame(key_resource_table)
knitr::kable(df_key_resource_table, format = "html", booktabs = TRUE)
```

@@

This work was funded by the Wellcome Trust (214337/Z/18/Z).
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 101020792).
KJ has been supported by a JSPS Postdoctoral fellowhip, LAYG by a BBSRC Discovery fellowship (BB/W010305/1), PS by a Wellcome Trust Institutional Strategic Support Award (204909/Z/16/Z), and KCAW by the EPSRC Hub for Quantitive Modelling in Healthcare (EP/T017856/1).
